## fireStrat Package
## by Kyle Doherty

## Introduction

The fireStrat package assists in the stratification and sampling of a high severity fires. Briefly, it creates a specified number of partitions for the following environmental variables: elevation, slope, and winter solstice insolation and identifies representative points within for sampling. 

## Installation
Users may download and install the fireStrat package from a Github repository as demonstrated below:

```{r, eval=F}
if (!require("devtools"))
  install.packages("devtools")
  library(devtools)

install_github(repo = "mosscoder/fireStrat")
```

## Usage

The user must first load a digital elevation model for the region of interest, the rdnbr fire severity layer, and a roads layer for the region.

```{r, echo=FALSE}
library(raster)
library(rgdal)

dem <- raster("hdr.adf")
rdnbr <- raster("az3532911160120100620_20090709_20110613_rdnbr.tif")
road <- readOGR(dsn = "MVUM_Roads.shp", layer = "MVUM_Roads")
```

Next the user calls the fireStrat() function, specifying the above layers, the desired number of zones (minimum of 5 maximum of 18), number of backup points within each of those zones, and mean winter solstice temperature for the region (dec.t argument). The latter is needed for the production of the winter solstice insolation model. Suitable average temperature data may be drawn from: http://www.ncdc.noaa.gov/cdo-web/search?datasetid=GHCNDMS. 

```{r, echo=FALSE}
library(fireStrat)

fireStrat(dem = dem, rdnbr = rdnbr, road = road, dec.t = 0, zones = 5, backups = 2)
```

By default the cutoff value for the fire severity raster is 643, though this may be adjusted with the cutoff argument as follows:

```{r, echo=FALSE}
fireStrat(dem = dem, rdnbr = rdnbr, road = road, dec.t = 0, zones = 5, backups = 2, cutoff = 700)
```

By default the output pdf map is 36" x 36". The user may adjust the output pdf map dimensions in inches with the map.height and map.width arguments as follows:

```{r, echo=FALSE}
fireStrat(dem = dem, rdnbr = rdnbr, road = road, dec.t = 0, zones = 5, backups = 2, map.width = 20, map.height = 40)
```

## Products

The fireStrat() function generates the following files in your working directory:

**buffer.elevation.tif** - a DEM raster layer for the buffered area  
**buffer.insolation.tif** - a winter solstice insolation raster layer for the buffered area  
**buffer.slope.tif** - a slope raster layer for the buffered area  
**env.cover.x.pdf** - three plots depicting partitions and sampling points in bivariate environmental space  
**stratified.espace.csv** - a table of all map grid cells within the buffered area containing coordinates, environmental values, and zone assignments  
**site_map.pdf** - a static map of the zones and sampling sites with road and contour overlays  
**sampling.points.csv** - a table containing sampling point ID's, coordinates, and environmental values  
**sampling_points.gpx** - a gpx file to load sampling points into Google Earth or similar program  
**zones.kmz** - a kmz file to load zones into Google Earth or similar program  




